### 2008-12-20 talk/ecoop2009/clibackend.tex
small tweaks in the flexswitch section, kill a section that we decided not to write

For instance, the code\footnote{For simplicity we write C\# code instead of
the actual IL bytecode.} generated for the dispatcher of method \texttt{0x0002}
is similar to the following fragment: 
\begin{small}
\begin{lstlisting}[language={[Sharp]C}]
// dispatch block
int methodid = (blockid && 0xFFFF0000) >> 16; 
int blocknum = blockid && 0x0000FFFF;         
if (methodid != MY_METHOD_ID) {
  // jump_to_ext 
  ...
}
switch(blocknum) {
  case 0: goto block0;
  case 1: goto block1;
  default: throw new Exception("Invalid block id");
}
\end{lstlisting}
\end{small}
If the next block to be executed is implemented in the same method
({\small\lstinline{methodid == MY_METHOD_ID}}), then the appropriate
jump to the corresponding code is executed.
Otherwise, the \lstinline{jump_to_ext}
part of the dispatcher has to be executed.
The code that actually jumps to an external block is contained in
the dispatcher of the primary method, whereas the
\lstinline{jump_to_ext} code of dispatchers of secondary methods
simply delegates the dispatcher of the primary method of the same
graph (see later).

@@

\subsection{Alternative implementations}
\dacom{need to be discussed with Antonio}

\anto{I propose to wait until the rest of paper is more or less in a final
  state, and see how much space is left}

\commentout{
Before implementing the solution described here, we carefully studied a lot of possible alternatives, but all of them either didn't work because of a limitation of the virtual machine or they could work but with terrible performances.

In particular, in theory it is possible to implement external links using tail calls, by putting each block in its own method and doing a tail call instead of a jump; this would also solve the problem of how to pass arguments, as each method could have its own signature matching the input args of the block. I would like to explain this solution in a more detailed way as I think it's really elegant and nice.

In theory, if the .NET JIT were smart enough it could inline and optimize away the tail calls (or at least many of those) and give us very efficient code. However, one benchmark I wrote shows that tail calls are up to 10 times slower (!!!) than normal calls, thus making impractical to use them for our purposes.
}

>>>>

The code\footnote{For simplicity we write C\# code instead of
the actual IL bytecode.} generated for the dispatcher of methods
is similar to the following fragment: 
\begin{small}
\begin{lstlisting}[language={[Sharp]C}]
// dispatch block
int methodid = (blockid && 0xFFFF0000) >> 16; 
int blocknum = blockid && 0x0000FFFF;         
if (methodid != MY_METHOD_ID) {
  // jump_to_ext 
  ...
}
switch(blocknum) {
  case 0: goto block0;
  case 1: goto block1;
  default: throw new Exception("Invalid block id");
}
\end{lstlisting}
\end{small}
If the next block to be executed is implemented in the same method
({\small\lstinline{methodid == MY_METHOD_ID}}), then the appropriate
jump to the corresponding code is executed.
Otherwise, the \lstinline{jump_to_ext}
part of the dispatcher has to be executed, which is implemented differently 
by primary and secondary methods.

@@
